Refactoring of Application Using Relational Database

### 2013-02-15 doc/paper.tex
added inheritance

\subsection{Application Model}
Application is defined as a sequence of classes and it creates the context for all structures used in the software persistent layer:
\begin{align}
& \mathbf{Application} = (Class*) \\
& 	\mathbf{Class} = (label, Property*, Association*) \\
& \mathbf{Property} = (label, AppType, DefaultValue, \nonumber \\ & \;\;\;\;  Cardinality, Mandatory) \\
&	\mathbf{Association} = (label, classRef, startCardinality, endCardinality)  \\
& \mathbf{AppType} = APPSTRING
\end{align}

@@

\subsection{Application Manipulation}
\label{sec:app-evolution}
The application model defines only the structure of an application thus there are defined transformation for its creating, altering and removing parts of the model (the set $A$). The conditions for successful transformations are simple in case of creating or altering:
\begin{enumerate}
	\item The name collisions has to be prevent when creating an class in the model or altering its name.
	\item All references have to be updated when renaming a class.
	\item The existence of referenced class has to be verified when creating or altering an association.  
\end{enumerate}
The only issue during deleting classes etc. from an application is the class can be removed only in case it is not associated by other classes. The transformations from $A$ are in table \ref{tab:app-evolution}. The list of altering operations is not complete as there are missing transformation for changing the obligation or cardinality of properties and associations. It is because these transformations are not so important for complex refactorings. 
\begin{table}
\caption{The transformations for application evolution.}
	\label{tab:app-evolution}
\centering
	\begin{tabular}{ll}
	\hline
	Type of transformation & Defined transformations \\
	\hline
	\\[-2ex] 
	Application Creation
	& newProperty(className, property, application) \\
	& newAssociation(className, association, mapping, \\ &  \hspace{0.5in}application) \\
	&  newClass(class, application) \\
	Application Alternation
		& renameProperty(className, oldName, newName, \\ &  \hspace{0.5in} application) \\
		& renameAssociation(className, oldName, newName, \\ &  \hspace{0.5in}application) \\
		& renameClass(oldName, newName, application)\\
		& changeReference(referncedClass, newReferencedClass) \\
	Application Disassembly 
		& removeProperty(className, propertyName,\\ &  \hspace{0.5in} application) \\
		& removeAssociation(className, associationName, \\ &  \hspace{0.5in}application) \\
		& removeClass(className, application)\\
	Copy Structure
		& copyProperty(sourceClass, property, targetClass,\\ &  \hspace{0.5in} newName, application)  \\
		& copyClass(class, newName, application) \\
	\hline
	\end{tabular}

\end{table}

@@

	removeClass & dropEmptyTable\\
	\hline
	\end{tabular}
\end{table}
The transformations for data-secure removal are used as default removing transformations, although the classic drop- transformations can be used. This should lead to the more careful usage of removing trnasformations.

@@

>>>>

\subsection{Application Model}
Application is defined as a sequence of classes and it creates the context for all structures used in the software persistent layer:
\begin{align}
& \mathbf{Application} = (Class*) \\
& 	\mathbf{Class} = (label, Property*, Association*, Inheritance) \\
& \mathbf{Property} = (label, AppType, DefaultValue, \nonumber \\ & \;\;\;\;  Cardinality, Mandatory) \\
&	\mathbf{Association} = (label, classRef, startCardinality, endCardinality)  \\
& \mathbf{Inheritance} = (class, InheritanceType) \\¨
& \mathbf{InheritanceType} = SINGLETABLE \; | \; TABLE-PER-CLASS \\
& \mathbf{AppType} = APPSTRING
\end{align}

@@

\subsection{Application Manipulation}
\label{sec:app-evolution}
The application model defines only the structure of an application thus there are defined transformation for its creating, altering and removing parts of the model (the set $A$). The conditions for successful transformations are simple in case of creating or altering:
\begin{enumerate}
	\item The name collisions has to be prevent when creating an class in the model or altering its name.
	\item All references have to be updated when renaming a class.
	\item The existence of referenced class has to be verified when creating or altering an association.  
\end{enumerate}
The only issue during deleting classes etc. from an application is the class can be removed only in case it is not associated by other classes. The transformations from $A$ are in table \ref{tab:app-evolution}. The list of altering operations is not complete as there are missing transformation for changing the obligation or cardinality of properties and associations. It is because these transformations are not so important for complex refactorings. 
\begin{table}
\caption{The transformations for application evolution.}
	\label{tab:app-evolution}
\centering
	\begin{tabular}{ll}
	\hline
	Type of transformation & Defined transformations \\
	\hline
	\\[-2ex] 
	Application Creation
	& newProperty(className, property, application) \\
	& newAssociation(className, association, mapping, \\ &  \hspace{0.5in}application) \\
	&  newClass(class, application) \\
	Application Alternation
		& renameProperty(className, oldName, newName, \\ &  \hspace{0.5in} application) \\
		& renameAssociation(className, oldName, newName, \\ &  \hspace{0.5in}application) \\
		& renameClass(oldName, newName, application)\\
		& changeReference(referncedClass, newReferencedClass) \\
		Application Disassembly 
		& removeProperty(className, propertyName,\\ &  \hspace{0.5in} application) \\
		& removeAssociation(className, associationName, \\ &  \hspace{0.5in}application) \\
		& removeClass(className, application)\\
	Copy Structure
		& copyProperty(sourceClass, property, targetClass,\\ &  \hspace{0.5in} newName, application)  \\
		& copyClass(class, newName, application) \\
	Inheritance manipulation   & setParent(class, parentClass) \\
		& removeParent(childClass) \\
		& pushDown(class, property)\\
		& pullUp(class, property)\\
	\hline
	\end{tabular}
\end{table}

@@

	removeClass & dropEmptyTable\\
	setParent & \\
	removeParent & \\
	pushDown &\\
	pullUp &\\
	\hline
	\end{tabular}
\end{table}
The transformations for data-secure removal are used as default removing transformations, although the classic drop- transformations can be used. This should lead to the more careful usage of removing transformations.

@@

\subsection{Inheritance Manipulation}
\begin{align}
& extractSuperClass(class, parentName, property*) \\
  & extractCommonSuperClass(firstClass, secondClass, parentName,  property* ) \\
\end{align}
